Understanding domestic abuse

### 2019-07-29 justification_of_resources.tex
Update justification_of_resources.tex

>>>>

PDRA Trendl. We request 100\% support for PDRA Trendl. A postdoctoral appointment is essential here, as the level of technical skill required to run and analyse these large and complex datasets is high. Furthermore, Trendl has extensive experience with these datasts, having already completed a project on the effects of Football tournaments on Domestic Abuse during her PhD. As outlined in Staff Duties, Trendl will conduct the statistical analyses and lead on the writing of the majority of publications. Trendl will also take an active role in impact activities, building upon existing relationships with WMP that were developed during her PhD research, and developing a network of contacts as this project supports her development as an Early Career Researcher.

PI Mullett. We request 15% support for Mullett. Half of this support will be spent on supporting the empirical work. This includes providing support and supervision to PDRA Trendl, as well as data management duties such as data cleaning, outputting from the highly sensitive data of appropriately sanitised/annonymised versions of the dataset for the other researchers. The other half of the support will be spent on impact activities. Academic faculty support is required to maximise the potential impact of the research. Mullett's existing relationships with WMP and membership of the Centre for Operational Policing Research are crucial in gaining the contacts and invitations to collaborate with policy makers and present research to relevant, decision making bodies.

CI Stewart. We request 10% support for Stewart. Stewart will aid in coordinating the research program. He will also meet regularly with the early career researcher Anna Trendl, providing insights and support---Stewart has extensive experience supervising postdoctoral researchers. A major role will also be to coordinate the communication of the results within the broader context of the Centre for Operational Policing Research (COPR) activities. This coordination, and the possibility for links and collaboration with other COPR members or projects will provide unique added value to the research. Stewart will contribute to the research design and writing academic papers.

We request funds for a data processing computer for use by PDRA Trendl. A high specification computer is critical for this work. The size of the datasets mean that a standard specification desktop computer often cannot even open the large data files, and the complexity of the required analysis means data processing can be prohibitively slow. Due to the sensitivity of the data being used, and the necessary security considerations, we cannot make use of other computing solutions as the researchers must maintain absolute control over the storage and access to the data.

We request support for regular trips to Birmingham, to facilitate ongoing collaboration and communication with partners at West Midlands Police HQ. In addition we request funding for travel to London to support the communication of results to national policy makers including contacts within the Metropolitan Police Service. We request support to attend academic conferences: we anticipate presenting the results at 2 European conferences, and 1 international conference. This will allow us to gain insight and input from other academic experts, and engage a wide range of academic beneficiaries.

Accumulating to Choose
